Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-07-12 edubots_surveys.Rnw
finishes adding questions to methodology refs #20

\textit{3. Which media features do you value the most for your interaction with your students?}
\begin{itemize}
\item Familiarity with its use i.e. that I do not need to learn a new tool
\item Familiarity i.e. that I do not need to learn a new tool
\item Admit the use of other means/toosl: blogs, chat groups in messaging platforms, any others.
\end{itemize}

>>>>

\textit{3. Which media features do you value the most for your interaction with your students?}
\begin{itemize}
\item Familiarity with its use i.e. that I do not need to learn a new tool
\item The official formation/training provided by your institution on its use
\item That only one-directional communication is allowed (from teachers to students)
\item Non-hierarchical tools that allowed teacher-to-student and student-to-student communication 
\item That allow additional functionalities such as interfaces to other tools
\item That allow teachers to develop/add their own functionalities (e.g. automatic correction tools)
\item That let me avoid to worry about maintenance and that it is easily sustainable from one year to the next
\item That allow to extract data to assess the student performance
\end{itemize}
